### 2017-01-02 2017mergingmerges/section/scrub.tex
start on fusion definition

%!TEX root = ../Main.tex
\section{Introduction}
\label{s:Introduction}

Fusion for array programs is important for removing intermediate arrays, reducing memory traffic as well as allocations.
However, when dealing with data too large to fit in memory such as tables on disk, removing intermediate arrays becomes essential rather than just desirable.
Attempting to create an intermediate array of such amounts of data would lead to thrashing and swapping to disk, or perhaps even running out of swap.
For these situations, some sort of assurance of total fusion is required: either the program can be fused with no intermediate arrays or unbounded buffers, or it will not compile at all.

Furthermore, existing systems for combinator fusion only support a subset of combinators, and only in limited cases.
Pull fusion supports joins where one combinator pulls from multiple inputs, but not splits where one output is used my multiple combinators.
Pull can thus express @merge@, but not @partition@.
Push fusion supports splits (@partition@), but not joins (@merge@).
Polarised fusion~\cite{lippmeier2016polarized} addresses these shortcomings by separating the computation into pull producers and push consumers, with explicit drain loops to convert between the two sections. However this requires manual plumbing.

We make the following contributions:
\begin{itemize}
\item a process calculus for streaming programs (\S\ref{s:Process});
\item some common combinators implemented as processes (\S\ref{s:Combinators});
\item and even more exotic combinators such as segmented operations (\S\ref{s:Combinators});
\item an algorithm for fusing pairs of processes (\S\ref{s:Fusion});
\item and a Coq proof of soundness (\S\ref{s:Proofs});
\end{itemize}

\section{Streams vs Push/Pull}

@@

>>>>

%!TEX root = ../Main.tex
\section{Streams vs Push/Pull}

@@

\subsection{Common}
\label{s:Combinators:Common}
